### 2012-05-19 trunk/GUIErrorDetector/paper/technique.tex
Tweak caption

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.40]{simplecg}
  \vspace*{-1.0ex}\caption {{\label{fig:simplecg} A simple call graph to illustrate the
invalid thread access problem. The \CodeIn{entry} method is executed
in a UI thread. Nodes \CodeIn{uiAcc1}, \CodeIn{uiAcc2}, and \CodeIn{uiAcc3} are
three UI-accessing methods. Node \CodeIn{safe} is a safe UI Method, and
node \CodeIn{start} is a (non-UI) thread-spawning method. Methods \CodeIn{uiAcc1}
and \CodeIn{uiAcc2} are executed in the UI thread, but method \CodeIn{uiAcc3}
is executed in a non-UI thread, causing an invalid thread access error.}}
\vspace{-2mm}
\end{figure}

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.40]{simplecg}
  \vspace*{-1.0ex}\caption {{\label{fig:simplecg} A simple call graph to illustrate the
invalid thread access problem. The \CodeIn{entry} method is executed
in the UI thread. Nodes \CodeIn{uiAcc1}, \CodeIn{uiAcc2}, and \CodeIn{uiAcc3} are
UI-accessing methods. Node \CodeIn{start} is a (non-UI)
thread-spawning method, and
node \CodeIn{safe} is a safe UI Method. Methods \CodeIn{uiAcc1}
and \CodeIn{uiAcc2} are executed in the UI thread, but method \CodeIn{uiAcc3}
is executed in a non-UI thread, causing an invalid thread access error.}}
\vspace{-2mm}
\end{figure}
